---
title: "MazeApp - Presentation"
author: "Joost Dijkstra Edward Tandia"
date: "2023-08-31"
output:
  powerpoint_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
devtools::install_github('Ed-sctt/RetakeExamF') # to edit ptds2022
library(RetakeExamF)
```

## Agenda

-   Project presentation & objectives

-   Package RetakeExamF

    -   Description
    -   Functions
    -   Maze App

-   Limitations & future work

## Project presentation (1)

-   The project is focused on building mazes. Exploring different algorithms related to the maze conception and conciliate these with R code.

## Proejct objectives (2)

-   The goal of this project is to develop an R package that generates mazes using various maze generation algorithms.

-   Create an interactive app where users can create their own maze and visualize the solution.

## Package RetakeExamF

### Description

RetakeExamF is a dynamic R package that empowers users to craft captivating mazes using the Depth-First Search (DFS) and Recursive Backtracking algorithms. The package provides a user-friendly platform to generate mazes of varying complexities.

```{r, echo = FALSE, out.height='25%', out.width='25%', fig.align='center'}
magick::image_read('./inst/img/package.svg')
```

*source :<https://freesvg.org/isometric-cardboard-box>*

## Recursive backtracking function

```{r echo=FALSE, fig.height=100, fig.width=100, fig.align= 'center'}
magick::image_read('./inst/img/rb_maze.gif')
```

This algorithm starts by creating a grid of cells and then repeatedly selects a cell to carve a path while backtracking to create dead-ends.

*source : <https://aryanab.medium.com/maze-generation-recursive-backtracking-5981bc5cc766>*

## Plot maze

```{r, echo = TRUE, eval=FALSE}
RetakeExamF::rb_maze(31,31) # maze generation
```

```{r echo = FALSE, fig.height=2, fig.width=2, fig.align='center'}
magick::image_read('./inst/img/rb_maze.png')
```

## Functions - myGraph() - plotmyMaze()

Example of the functions usage :

```{r, echo = TRUE, cache =TRUE, fig.height=3, fig.width=3, fig.align='center',eval=FALSE}
# myGraph() 
Example_maze <- RetakeExamF::myGraph (nrows = 5,ncols = 9) 
#plotmyMaze()
RetakeExamF::plotmyMaze(Example_maze,nrows= 5,ncols = 9)
```

```{r echo = FALSE, out.height='50%',out.width='50%', fig.align='center'}
magick::image_read('./inst/img/graph.png')
```

## Functions - dfs_method()

```{r echo = FALSE, fig.height=50, fig.width=50, fig.align='center'}
magick::image_read('./inst/img/dfs_gif.gif')
```

The algorithm Depth-First Search (DFS) is a graph traversal algorithm that explores as far as possible along a branch before backtracking.

source: [*https://miro.medium.com/v2/resize:fit:720/1\*unQanD3lFwpajj6lsJVw8g.gif*](https://miro.medium.com/v2/resize:fit:720/1*unQanD3lFwpajj6lsJVw8g.gif){.uri}

## Plot DFS

```{r cars, echo = TRUE, cache=TRUE,fig.height=3, fig.width=3, fig.align='center'}
#dfs_method()
Example_maze <- RetakeExamF::myGraph (nrows = 5,ncols = 9)
Example_maze<-RetakeExamF::dfs_method(GraphMade = Example_maze)

RetakeExamF::plotmyMaze(Example_maze,nrows= 5,ncols = 9)
```

## Functions - solverGraph()

```{r echo = TRUE, cache=TRUE,fig.height=3, fig.width=3, fig.align='center'}
# solver visualization
RetakeExamF::solverGraph(Example_maze,nrows= 5,ncols = 9)
```

## Functions - myMazeShinyApp3()

Example function that runs the app on shiny :

```{r, eval= FALSE}
RetakeExamF::myMazeShinyApp3() # shiny app experience 
```

```{r, echo = FALSE, out.height='90%', out.width='90%', fig.align='center'}
magick::image_read('./inst/img/mazeApp.png')
```

## Maze App

Now, let's run the app !

## Limitations & future work

### Limitations

-   Lack of user features - (i.e. walk around the maze )
-   Lack of creativity (try out different approaches)
-   Bottleneck issue when increasing the size of the maze

### Future work

-   More algorithm variety to build mazes
-   Homework assignment : Solve the maze
-   More interactivity ➡️ Create a game ?
