---
title: "MazeApp - Presentation"
author: "Joost Dijkstra Edward Tandia"
date: "2023-08-26"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
devtools::install_github('Ed-sctt/RetakeExamF') # to edit ptds2022
library(RetakeExamF)
```

## Agenda

-   Project presentation & objectives

-   Package RetakeExamF

    -   Description
    -   Functions
    -   Maze App

-   Limitations & future work

## Project presentation (1)

-   The project is focused on building mazes. Exploring different algorithms related to the maze conception and conciliate these with R code.

```{r echo = TRUE}

```

## Proejct objectives (2)

-   The goal of this project is to develop an R package that generates mazes using various maze generation algorithms.

-   Create an interactive app where users can create their own maze and visualize the solution.

## Package RetakeExamF

### Description

RetakeExamF is a dynamic R package that empowers users to craft captivating mazes using the Depth-First Search (DFS) algorithm. The package provides a user-friendly platform to generate mazes of varying complexities. 

```{r, echo = FALSE, out.height='25%', out.width='25%', fig.align='center'}
magick::image_read('img/package.svg')
```


## Joost function
To be continued...

## Functions - myGraph() - plotmyMaze()

Example of the functions usage :

```{r, echo = TRUE, cache =TRUE, fig.height=3, fig.width=3, fig.align='center'}
# myGraph() 
Example_maze <- RetakeExamF::myGraph (nrows = 5,ncols = 9) 
#plotmyMaze()
RetakeExamF::plotmyMaze(Example_maze,nrows= 5,ncols = 9)
```

## Functions - dfs_method()

```{r cars, echo = TRUE, cache=TRUE,fig.height=3, fig.width=3, fig.align='center'}
#dfs_method()
Example_maze<-RetakeExamF::dfs_method (GraphMade = Example_maze)

RetakeExamF::plotmyMaze(Example_maze,nrows= 5,ncols = 9)
```

## Functions - solverGraph()

```{r echo = TRUE, cache=TRUE,fig.height=3, fig.width=3, fig.align='center'}
# solver visualization
RetakeExamF::solverGraph(Example_maze,nrows= 5,ncols = 9)
```

## Functions - mymazeApp()

Example function that runs the app on shiny :
```{r, eval= FALSE}
RetakeExamF::myMazeShinyApp() # shiny app experience 
```

```{r, echo = FALSE, out.height='90%', out.width='90%', fig.align='center'}
magick::image_read('img/MazeApp.png')
```

## Maze App

Now, let's run the app ! 

## Limitations & future work
### Limtations 
  - DFS algorithm only, no other methods implemented
  - Lack of user features - (i.e. walk around the maze )
  - Lack of creativity (try out different approaches)
  - Bottleneck issue when increasing the size of the maze
  
### Future work
  - More algorithm variety to build mazes
  - More interactivity --> Create a game ? 